Words aren't created equal: Investigating bias on the CDI

### 2022-01-11 paper/cogsci.Rmd
writing

For each demographic dimension (sex, socioeconomic status, and ethnicity) we fit a separate Rasch model for each demographic group.

>>>>

In the multigroup Rasch model, an item's difficulty is allowed to vary depending on which group an individual child belongs to. 
For example, in the sex-based multigroup model, item $i$'s difficulty is $b_{i}^{female}$ for females, and $b_{i}^{male}$ for males.
We fitted a multigroup Rasch model for each demographic dimension (sex, socioeconomic status, and ethnicity).
